---
title: "best1634"
author: "GG"
date: "2/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(dbplyr)
```
```{r}
final_best <- read_csv("~/github/BEST_data/data/fish_tidy_best.csv")
head(final_best)
final_best[ final_best == 0] <-NA
```

Contrtibute of each trophic guild to biomass at each site
```{r}
trophic_guilds_sites <- ggplot(data = final_best, aes(x = site, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "fill") + scale_fill_brewer(palette = "Dark2") + scale_y_continuous(name = "Percent Biomass", labels=c("0", "25", "50", "75", "100")) + theme_bw() + labs(x="")
ggsave(filename = "best_trophic_guilds_sites.eps", plot = trophic_guilds_sites, device = "eps", path = "~/github/BEST_data")
trophic_guilds_sites
```

```{r}
trophic_guilds_time <- ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "fill") + scale_fill_brewer(palette = "Dark2") + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + scale_y_continuous(name = "Percent Biomass", labels=c("0", "25", "50", "75", "100")) + theme_bw() + labs(x="")
ggsave(filename = "best_trophic_guilds_time.eps", plot = trophic_guilds_time, device = "eps", path = "~/github/BEST_data")
trophic_guilds_time
```

```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "stack") + scale_fill_brewer(palette = "Dark2") + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + theme_bw() + labs(y="Mean Biomass(g)")

```


Mean biomass of each trophic group per survey per site
```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "fill") + scale_fill_brewer(palette = "Dark2") + facet_grid(site~., scales = "free") + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + scale_y_continuous(name = "Percent Biomass", labels=c("0", "25", "50", "75", "100"))+ theme_bw()
```


```{r}
anovatg <- aov(sqrt(biomass) ~ as.character(trophic_guild) * site * as.character(survey), data = final_best)
summary.aov(anovatg)
TukeyHSD(anovatg)
```
```{r}
plankto_bio <- subset(final_best, trophic_guild=="planktivore")
anovatgpbio <- aov(sqrt(biomass) ~ site + as.character(survey), data = plankto_bio)
summary.aov(anovatgpbio)
TukeyHSD(anovatgpbio)
```
```{r}
carno_bio <- subset(final_best, trophic_guild=="macro_carnivore")
anovatgcbio <- aov(sqrt(biomass) ~ site + as.character(survey), data = carno_bio)
summary.aov(anovatgcbio)
TukeyHSD(anovatgcbio)
```

```{r}
inverto_bio <- subset(final_best, trophic_guild=="invertivore")
anovatgibio <- aov(sqrt(biomass) ~ site + as.character(survey), data = inverto_bio)
summary.aov(anovatgibio)
TukeyHSD(anovatgibio)
```

```{r}
herbi_bio <- subset(final_best, trophic_guild=="herbivore")
anovatghbio <- aov(sqrt(biomass) ~ site + as.character(survey), data = herbi_bio)
summary.aov(anovatghbio)
TukeyHSD(anovatghbio)
```

```{r}
omni_bio <- subset(final_best, trophic_guild=="omnivore")
anovatgobio <- aov(sqrt(biomass) ~ site + as.character(survey), data = omni_bio)
summary.aov(anovatgobio)
TukeyHSD(anovatgobio)
```

```{r}
biomass_by_time <- ggplot(data = final_best, aes(x = survey, y=biomass, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Mean Biomass (g)") + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + stat_summary(geom = "errorbar", fun.data = mean_se) + theme_bw() + theme(legend.position = "none")
ggsave(filename = "best_biomass_by_time.eps", plot = biomass_by_time, device = "eps", path = "~/github/BEST_data")
biomass_by_time
```


```{r}
density_by_time <- ggplot(data = final_best, aes(x = survey, y=density, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Mean Density (no/30m^2)") + stat_summary(geom = "errorbar", fun.data = mean_se) + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + theme_bw() + theme(legend.position = "none")
ggsave(filename = "best_density_by_time.eps", plot = density_by_time, device = "eps", path = "~/github/BEST_data")
density_by_time
```

```{r}
biomass_site <- ggplot(data = final_best, aes(x = survey, y=biomass, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Mean Biomass (g)") + facet_grid(.~site, scales = "free") + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) + theme_bw() 
ggsave(filename = "best_biomass_by_site.eps", plot = biomass_site, device = "eps", path = "~/github/BEST_data")
biomass_site
```

Anova analysis on overall biomass between surveys and sites: data square root transformed to meet the assumptions

```{r}
anova1 <- aov(sqrt(biomass) ~ as.character(survey) * site, data = final_best)
summary.aov(anova1)
TukeyHSD(anova1)
```

```{r}
ggplot(data = final_best, aes(x = survey, y=density, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Mean Density (n/30m2)") + facet_grid(.~site, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) 
```


```{r}
anovaden <- aov(sqrt(density) ~ as.character(survey) * site, data = final_best)
summary.aov(anovaden)
TukeyHSD(anovaden)
```


```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean") + facet_grid(trophic_guild~site, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) 
```

```{r}
ggplot(data = final_best, aes(x = site, y=biomass, fill = site)) + geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + facet_grid(survey~trophic_guild, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se)  
```

```{r}
ggplot(data = final_best, aes(x = site, y=biomass, fill = site)) + geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + facet_grid(trophic_guild~survey, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se)  
```

```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + facet_grid(.~site, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") + scale_y_log10()
```

```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", ) + facet_grid(.~site, scales = "free") + scale_y_log10()
```

```{r}
ggplot(data = final_best, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "fill") + facet_grid(.~site, scales = "free") + labs(y = "% biomass") + scale_x_discrete(name = "survey", limit=c("1", "2", "3", "4", "5", "6")) + theme_bw()
```

```{r}
ggplot(data = final_best, aes(x = survey, y=density, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean", position = "fill") + facet_grid(.~site, scales = "free") + labs(y = "% biomass") + scale_x_discrete(name = "survey", limit=c("1", "2", "3", "4", "5", "6")) + theme_bw()
```

```{r}
final_best_clean <- filter(final_best, biomass>0)
```


```{r}
best_matrix <- final_best_clean %>% group_by(survey, site, species)
```
```{r}
best_matrix2 <- summarise(best_matrix, bio = mean(biomass), den = mean(density))
```
```{r}
matrix_best_pcoa <- read_csv("~/github/BEST_data/data/percent_bio_clean.csv")
library(tidyr)
# The arguments to spread():
# - data: Data object
# - key: Name of column containing the new column names
# - value: Name of column containing values
matrix_wide_pcoa <- spread(matrix_best_pcoa, species, percent_bio)
matrix_wide_pcoa
```

```{r}

matrix_wide_pcoa[is.na(matrix_wide_pcoa)] <-0
matrix_wide_pcoa

```

```{r}
matrix_wide_pcoa$id <- c("HS1_1", "NNE_1", "XL_1", "HS1_2", "NNE_2", "XL_2", "XL_3", "HS1_4", "XL_4", "HS1_5", "NNE_5", "XL_5", "HS1_6", "NNE_6", "XL_6")
matrix_wide_pcoa
```
```{r}
library(tidyverse)
#need to figure out the row name issue
matrix_wide_pcoa[1] = NULL
matrix_wide_pcoa[1] = NULL
row.names(matrix_wide_pcoa) <- matrix_wide_pcoa$id
matrix_wide_pcoa$id = NULL
```

```{r}
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra)
```


```{r}
library(ggplot2)
cluster_best <- kmeans(matrix_wide_pcoa[,-1], centers = 3, nstart = 25)
str(cluster_best)
pcaplot <- fviz_cluster(cluster_best, data = matrix_wide_pcoa[,-1], fill = "darkblue") + ylim(-2.5,4.5) + theme_classic()
pcaplot
```
```{r}
library(vegan)

```


```{r}
# apply PCA - scale. = TRUE is highly 
# advisable, but default is FALSE. 
pca_best <- prcomp(matrix_wide_pcoa[,-1],
                 center = TRUE,
                 scale. = TRUE) 
```
plotting pricipal component analysis
```{r}
autoplot(pca_best, data = matrix_wide_pcoa, label = TRUE, colour = 'site')
```
Adding 
```{r}
library(ggfortify)
pca.plot2 <- autoplot(pca_best, data = matrix_wide_pcoa, colour = 'site', frame = TRUE, frame.type = "convex")
pca.plot2
ggsave(filename = "best_pcaplot_convex.eps", plot = pca.plot2, device = "eps", path = "~/github/BEST_data")
```

```{r}
pam_plot <- fviz_pca_ind(pca_best, label="none", habillage=matrix_wide_pcoa$site,
     addEllipses=TRUE, ellipse.level=0.95, palette = "Dark2") + theme_classic()
pam_plot
ggsave(filename = "best_pcaplot_conf.eps", plot = pam_plot, device = "eps", path = "~/github/BEST_data")
```

```{r}
best_heatmap <- ggplot(data = matrix_best_pcoa, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, percent_bio, mean, order = TRUE), fill = percent_bio), color = "navyblue", width = 0.85) +
  scale_fill_gradient2(low = "snow", high = "navyblue", mid = "steelblue", midpoint = 0.375) +
  ylab("Species") +
  xlab("Site") +  
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(fill = "Percent Biomass")
ggsave(filename = "best_heatmap_blue.eps", plot = best_heatmap, device = "eps", path = "~/github/BEST_data")
```
```{r}
best_heatmap_bupu <- ggplot(data = matrix_best_pcoa, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, percent_bio, mean, order = TRUE), fill = percent_bio), color = "navyblue", width = 0.85) +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(8, "BuPu")) +
  ylab("Species") +
  xlab("Site") +  
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(fill = "Percent Biomass")
ggsave(filename = "best_heatmap_bupu.eps", plot = best_heatmap_bupu, device = "eps", path = "~/github/BEST_data")
```


```{r}
best_heatmap_red <- ggplot(data = matrix_best_pcoa, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, percent_bio, mean, order = TRUE), fill = percent_bio), color = "tomato4", width = 0.85) +
  scale_fill_gradient2(low = "snow", high = "tomato4", mid = "tomato3", midpoint = 0.375) +
  ylab("Species") +
  xlab("Site") +  
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(fill = "Percent Biomass")
ggsave(filename = "best_heatmap_red.eps", plot = best_heatmap_red, device = "eps", path = "~/github/BEST_data")
```
```{r}
best_heatmap_den_blu <- ggplot(data = best_matrix2, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, den, mean, order = TRUE), fill = log(den)), color = "navyblue", width = 0.85) +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9, "BuPu")) +
  ylab("Species") +
  xlab("Site") +  
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(fill = "Density")
ggsave(filename = "best_heatmap_den_blu.eps", plot = best_heatmap_den_blu, device = "eps", path = "~/github/BEST_data")
```
```{r}
best_heatmap_den_red <- ggplot(data = best_matrix2, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, den, mean, order = TRUE), fill = log(den)), color = "red4", width = 0.85) +
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9, "Reds")) +
  ylab("Species") +
  xlab("Site") +  
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(fill = "Density")
ggsave(filename = "best_heatmap_den_red.eps", plot = best_heatmap_den_red, device = "eps", path = "~/github/BEST_data")
best_heatmap_den_red
```

```{r}
demog_best <- read_csv("~/github/BEST_data/data/best_tidy_demog.csv")
head(demog_best)
```

```{r}
histo_by_site <- ggplot(data = demog_best[-301,], aes(tl_cm, fill = site)) + geom_histogram(bins = 10) + scale_fill_brewer(palette = "Dark2") + facet_grid(site~.) + scale_x_continuous(name = "Size Class", breaks = seq(15, 45, 5)) + theme_bw() + ylab("Percent")
ggsave(filename = "best_histo_by_site.eps", plot = histo_by_site, device = "eps", path = "~/github/BEST_data")
histo_by_site
```
```{r}
histo_by_sex <- ggplot(data = demog_best[-301,], aes(tl_cm, fill = sex)) + geom_histogram(bins = 10, position = "dodge") + scale_fill_brewer(palette = "Set1") +  scale_x_continuous(name = "Size Class", breaks = seq(15, 45, 5)) + theme_bw() + ylab("Percent")
ggsave(filename = "best_histo_by_sex.eps", plot = histo_by_sex, device = "eps", path = "~/github/BEST_data")
histo_by_sex
```


```{r}
histo_overall <- ggplot(data = demog_best[-301,], aes(tl_cm)) + geom_histogram(bins = 10, fill = "royalblue3", colour = "black") +  scale_x_continuous(name = "Size Class", breaks = seq(10, 50, 5)) + theme_bw() + ylab("Percent")
ggsave(filename = "best_histo_overall.eps", plot = histo_overall, device = "eps", path = "~/github/BEST_data")
histo_overall
```



```{r}
#mean size by site and sex
meansize_sex_site <- ggplot(data = demog_best[-301,], aes(x = sex, y = tl_cm, fill = sex)) + geom_boxplot() + scale_fill_brewer(palette = "Set1") + theme_classic() + ylab("Total Length (cm)") + xlab("Sex") + theme(legend.position = "none")
ggsave(filename = "meansize_sex.eps", plot = meansize_sex_site, device = "eps", path = "~/github/BEST_data")
meansize_sex_site
```

```{r}
#mean size by site only
meansize_site <- ggplot(data = demog_best[-301,], aes(x = site, y = tl_cm, fill = site)) + geom_boxplot() + scale_fill_brewer(palette = "Set1") + theme_classic() + ylab("Total Length (cm)") + xlab("Site") + theme(legend.position = "none")
ggsave(filename = "meansize_site.eps", plot = meansize_site, device = "eps", path = "~/github/BEST_data")
meansize_site
```
```{r}
ggplot(data = demog_best[-301,], aes(x = date, y = tl_cm, fill = date)) + geom_bar(stat = "summary", fun.y = "mean") + theme_classic() + ylab("Total Length (cm)") + xlab("Site") + theme(legend.position = "none") 
```

```{r}
ggplot(data = demog_best[-301,], aes(x = site, fill = sex)) + geom_bar(position = "fill", color = "black") + theme_classic() + scale_fill_brewer(palette = "Set1") + ylab("Percent") + xlab("")
ggsave(filename = "sex_ratio.eps", device = "eps", path = "~/github/BEST_data")
```
```{r}

lionfish_best <- read_csv("~/github/BEST_data/data/lionfish_data_2019.csv")
head(lionfish_best)
```

```{r}
lf_density_by_time <- ggplot(data = lionfish_best, aes(x = survey, y=lf_quad, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Lionfish Density (no/250m^2)/Lionfsh Removed") + stat_summary(geom = "errorbar", fun.data = mean_se) + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + theme_bw() + geom_line(aes(x = survey, y = lf_removed, color = site)) 
ggsave(filename = "lf_density_by_time.eps", plot = lf_density_by_time, device = "eps", path = "~/github/BEST_data")
lf_density_by_time
```
```{r}
efficiency <- ggplot(data = lionfish_best, aes(x = efficiency, y = lf_density)) + geom_point() + geom_smooth(method='lm',formula=y~x) + theme_classic() + xlab("Lionfish Density (no/hectare)") + ylab("Culling Efficiency")

efficiency
```
```{r}
ggsave(filename = "efficiency.eps", plot = efficiency, device = "eps", path = "~/github/BEST_data")
```



```{r}
lionfish_best.2 <- read_csv("~/github/BEST_data/data/lionfish_data_2.csv")
#time for the correlation matrix
library(tidyverse)
library(ggcorrplot)
corrdata <- lionfish_best.2
corrdata$date = NULL 
corrdata$lf_quad = NULL
corrdata$lf_removed = NULL
corrdata$sst = NULL
corrdata$site = NULL
corrdata$lunar_day = NULL
corrdata$survey = NULL
corrdata$efficiency = NULL
head(corrdata)
```
```{r}
best_corr <- round(cor(corrdata), 1)

```
```{r}
p.mat <- cor_pmat(corrdata)
p.mat
```

```{r}
best_corr_plot <- ggcorrplot(best_corr, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, outline.col = "white",
           p.mat = p.mat,
           title="Correlation Matrix", 
           colors = c("steelblue4", "white", "red"),
           ggtheme=theme_bw)
best_corr_plot
```

```{r}
ggsave(filename = "correlation_matrix.eps", plot = best_corr_plot, device = "eps", path = "~/github/BEST_data")
```

```{r}
library(devtools)
library(ggbiplot)
library(ggfortify)
```


```{r}
best.pca <- corrdata[,-1]
d.factanal.best <- factanal(best.pca, factors = 2, scores = 'regression')
pca.plot.best <- autoplot(d.factanal.best, data = corrdata, colour = 'lf_density', size = 4,
         loadings = TRUE, loadings.label = TRUE, loadings.label.size  = 5) + theme_classic()
pca.plot.best
```
```{r}
ggsave(filename = "factanal_pca.eps", plot = pca.plot.best, device = "eps", path = "~/github/BEST_data")
```
GLM model with all variables included showing covariance among possible drivers. 
```{r}
scale((corrdata[,-1]), center = TRUE, scale = TRUE)
fit.best <- glm((lf_density)~prey_density+kg_30m2+bt+temp_diff+prev_removed, data=corrdata, family = Gamma())
summary(fit.best)
```
Testing covairance
```{r}
#install.packages('data.table')
library(car)
sqrt(vif(fit.best))
```
*using Gamma distribution as this model results in the most "normal" data, see plots below of model fits*  
```{r}
scale((corrdata[,-1]), center = TRUE, scale = TRUE)
fit_den.best <- glm((lf_density)~prey_density, data=corrdata, family = Gamma)
fit_bio.best <- glm((lf_density)~kg_30m2, data=corrdata, family = Gamma)
fit_btemp.best <- glm((lf_density)~bt, data=corrdata,family = Gamma)
fit_tempdiff.best <- glm((lf_density)~temp_diff, data=corrdata,family = Gamma)
fit_culled.best <- glm((lf_density)~prev_removed, data=corrdata, family = Gamma)
AIC(fit_den.best, fit_bio.best, fit_btemp.best, fit_tempdiff.best, fit_culled.best)
coef(fit_den.best, fit_bio.best, fit_btemp.best, fit_tempdiff.best, fit_culled.best)
summary(fit_den.best)
summary(fit_bio.best)
summary(fit_btemp.best)
summary(fit_tempdiff.best)
summary(fit_culled.best)
```


```{r}
culling_effect <- ggplot(data = lionfish_best.2[4:15,], aes(x = prev_removed, y = lf_removed/day_unculled)) + geom_point() + geom_smooth(method='lm',formula=y~x) + theme_classic() + ylab("Rate of Recolonisation (#/day)") + xlab("Initial Density")

lm_eqn <- function(lionfish_best.2){
    m <- lm(lf_removed/day_unculled ~ prev_removed, lionfish_best.2[4:15,]);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2),
              b = format(coef(m)[2], digits = 2),
             r2 = format(r2, digits = 3)))
    as.character(as.expression(eq));
}
culling_effect1 <- culling_effect + geom_text(x = 25, y = 2, label = lm_eqn(lionfish_best.2), parse = TRUE)
culling_effect1
scale((corrdata[,-1]), center = TRUE, scale = TRUE)
colonisation_corr <- glm((lf_removed/day_unculled)~prev_removed, data=corrdata)
summary(colonisation_corr)
library(vegan)
r2 <- RsquareAdj(colonisation_corr)
r2
```




```{r}
ggsave(filename = "recolonization_density.eps", plot = culling_effect, device = "eps", path = "~/github/BEST_data")
```
```{r}
lf_efficiency <- ggplot(data = lionfish_best.2[4:15,], aes(x = survey, y=(((lf_removed)/day_unculled)), fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Daily Rate of Recolonisation") + stat_summary(geom = "errorbar", fun.data = mean_se) + scale_x_discrete(name = "Survey Number", limits=c("1", "2", "3", "4", "5", "6")) + theme_bw() + theme(legend.position = "none")

lf_efficiency
```
```{r}
ggsave(filename = "recolonization_survey.eps", plot = lf_efficiency, device = "eps", path = "~/github/BEST_data")
```

```{r}
lf_recolonization <- ggplot(data = lionfish_best.2[4:15,], aes(x = site, y=(((lf_removed)/day_unculled)), fill = site)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Daily Rate of Recolonisation") + stat_summary(geom = "errorbar", fun.data = mean_se) + theme_bw() 

lf_recolonization
```

```{r}
ggsave(filename = "recolonization_site.eps", plot = lf_recolonization, device = "eps", path = "~/github/BEST_data")
```
```{r}
lf_recolonization.2 <- ggplot(data = lionfish_best.2[4:15,], aes(x = survey, y=(((lf_removed)/day_unculled)), fill = site)) + geom_bar(stat = "summary", fun.y = "mean") + labs(y = "Daily Rate of Recolonisation") + stat_summary(geom = "errorbar", fun.data = mean_se) + facet_grid(site~., scales = "free") + theme_bw() 
lf_recolonization.2
```

```{r}
anovarecol <- aov(sqrt(lf_removed/day_unculled) ~ site*survey, data = lionfish_best.2)
summary.aov(anovarecol)

```

```{r}
anovarecol.site <- aov(sqrt(lf_removed/day_unculled) ~ site, data = lionfish_best.2)
summary.aov(anovarecol.site)

```

```{r}
library(dplyr)
```
```{r}
lionfish_best.2 %>%

summarise(avg = mean((lf_removed/day_unculled)), sd(lf_removed/day_unculled))
```
```{r}
lionfish_best.2[4:15,] %>%
group_by(survey) %>%
summarise(avg = mean((lf_removed/day_unculled)), sd(lf_removed/day_unculled))
```

