---
title: "BEST_fish_tidy"
author: "GG"
date: "4/12/2018"
output: html_document
---
```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(dbplyr)
```

```{r}
final_fish2 <- read_csv("~/Documents/fish_tidy2.csv")
head(final_fish2)

```

Mean biomass of each trophic group per survey per site
```{r}
ggplot(data = final_fish2, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean") + facet_grid(site~., scales = "free")
```

```{r}
ggplot(data = final_fish2, aes(x = survey, y=biomass, fill = site)) + geom_bar(stat = "summary", fun.y = "mean") + facet_grid(site~., scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) 
```

Anova analysis on overall biomass between surveys and sites: data square root transformed to meet the assumptions

```{r}
anova1 <- aov(sqrt(biomass) ~ as.character(survey) * site, data = final_fish2)
summary.aov(anova1)
TukeyHSD(anova1)
```

##Results
1. Significant differences by site and by survey but not by the interaction, i.e. all sites follow the same trend. 
2. Biomass is significantly higher at NNE than HS1 and XL, the latter do not differ. 
2. Biomass is significantly higher at the first time point compared to surveys 4, 5, and 6
2. Biomass at the second time point is the same as the first but higher than survey 5. 
*Need to confirm data meets assumptions after transformation*

```{r}
ggplot(data = final_fish2, aes(x = survey, y=biomass, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean") + facet_grid(trophic_guild~site, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) 
```

```{r}
anova2 <- aov(sqrt(biomass) ~ site * trophic_guild, data = final_fish2)
summary.aov(anova2)
TukeyHSD(anova2)
```

#Reuslts
1. Significant differences in biomass of each trophic guild by site
2. Significantly more carnivores than invtertivores, omnivores and herbivores overall
3. Significanlty more planktivores than invertivores, omnivores and herbivores overall
4. No difference between biomass of carnivores and planktivores
5. NNE has significantly more planktivores and more carnivores than HS1
6. NNE has significatnly more carnivores and planktivores than herbivores and invertivores
7. XL has significantly more carnivores and planktivores than invertivores. 

```{r}
ggplot(data = final_fish2, aes(x = survey, y=biomass, color = survey)) + geom_point(stat = "summary", fun.y = "mean") + facet_grid(trophic_guild~site, scales = "free") + theme(legend.position = "none") + stat_summary(geom = "errorbar", fun.data = mean_se) + scale_y_log10()
```

```{r}
ggplot(data = final_fish2, aes(x = survey, y=biomass, fill = survey)) + geom_bar(stat = "summary", fun.y = "mean") + stat_summary(geom = "errorbar", fun.data = mean_se) + geom_line(stat = "summary", fun.y = "mean") + theme(legend.position = "none")
```


```{r}
ggplot(data = final_fish2, aes(x = survey, y=density, fill = trophic_guild)) + geom_bar(stat = "summary", fun.y = "mean") + facet_grid(site~., scales = "free") 
```
```{r}

ggplot(data = final_fish2, aes(x = trophic_guild, y = density, fill = trophic_guild)) + geom_boxplot() + theme(legend.position = "none") + scale_y_log10()
```


```{r}

ggplot(data = final_fish2, aes(x = trophic_guild, y = biomass, fill = trophic_guild)) + geom_boxplot() + scale_y_log10() + facet_grid(site~., scales = "free") 

```

```{r}

ggplot(data = final_fish2, aes(x = trophic_guild, y = density, fill = trophic_guild)) + geom_boxplot() + scale_y_log10() + facet_grid(site~., scales = "free") 

```

```{r}

ggplot(data = final_fish2, aes(x = trophic_guild, y = biomass, fill = trophic_guild)) + geom_boxplot() + theme(legend.position = "none") + scale_y_log10()
```

```{r}
anova4 <- aov(sqrt(density) ~ as.character(survey) * site/trophic_guild, data = final_fish2)
summary.aov(anova4)
TukeyHSD(anova4)
```


##Results anova 4
1. Significant differences by site and by survey but not by the interaction, i.e. all sites follow the same trend. 
2. Density is significantly higher at NNE and XL than HS1. 
2. Density is significantly higher at the first and second time points compared to surveys 4, 5, and 6

*Need to confirm data meets assumptions after transformation*

```{r}
anova5 <- aov(sqrt(density) ~ trophic_guild, data = final_fish2)
summary.aov(anova5)
TukeyHSD(anova5)
```

```{r}
anova6 <- aov(sqrt(biomass) ~ trophic_guild, data = final_fish2)
summary.aov(anova6)
TukeyHSD(anova6)
```

#Results Anova 5 and 6
1. Higher density of planktivores than any other trophic group. No difference among others
2. Higher biomass of carnivores and planktivores than all other groups. No difference between planktivores and carnivores. 






